---
title: "DATA INTEG MONTHLY"
author: "Kang Gyeonghun"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      root.dir = dirname(rstudioapi::getActiveDocumentContext()$path))
dirname(rstudioapi::getActiveDocumentContext()$path)
oldloc = Sys.getlocale("LC_ALL")
Sys.setlocale("LC_ALL", "korean")
```

<br>

**필요한 패키지들 불러오기**
```{r, results='hide', warning=FALSE, message=FALSE}
pkgs = c('tidyverse','ggplot2',"lubridate", "readxl", "data.table")
pkg_ins = rownames(installed.packages())
for(pkg in pkgs){  if(!(pkg %in% pkg_ins)) install.packages(pkg, character.only=T) }
sapply(pkgs, require, character.only=T)
```

서울코드 불러오기
```{r}
citycodes = fread("data/citycode.csv", encoding = "UTF-8")
seoulCode = rbind(citycodes[1:24,], tail(citycodes,1))
```

# Monthly analysis

## Target: FW18~20 Monthly

```{r}
DF = fread("data/fw1720_gu_imputed_weekly.csv", encoding = "UTF-8")
Month = as.Date(cut(DF$Week, "month"))
DF = aggregate(.~Month, DF[,-1], sum, na.action = NULL)
DF = DF %>% gather("gu", "FW_t", -Month) %>% filter(Month >= "2018-01-01" & Month < "2020-07-01") %>% arrange(gu, Month)
FW1820_mly = DF
FW1820_mly
```

시각화

```{r}
FW1820_mly %>% 
  filter(gu %in% sort(seoulCode$citySggName)[2:7]) %>% 
  ggplot()+
  geom_line(aes(x=ymd(Month), y=FW_t, color=gu))+
  facet_wrap(~ gu, scales="free")+
  theme(legend.position="right")+theme_bw()
ggsave("panel1.jpg")

FW1820_mly %>% 
  filter(gu %in% sort(seoulCode$citySggName)[8:13]) %>% 
  ggplot()+
  geom_line(aes(x=ymd(Month), y=FW_t, color=gu))+
  facet_wrap(~ gu, scales="free")+
  theme(legend.position="right")+theme_bw()
ggsave("panel2.jpg")

FW1820_mly %>% 
  filter(gu %in% sort(seoulCode$citySggName)[14:19]) %>% 
  ggplot()+
  geom_line(aes(x=ymd(Month), y=FW_t, color=gu))+
  facet_wrap(~ gu, scales="free")+
  theme(legend.position="right")+theme_bw()
ggsave("panel3.jpg")

FW1820_mly %>% 
  filter(gu %in% sort(seoulCode$citySggName)[20:25]) %>% 
  ggplot()+
  geom_line(aes(x=ymd(Month), y=FW_t, color=gu))+
  facet_wrap(~ gu, scales="free")+
  theme(legend.position="right")+theme_bw()
ggsave("panel4.jpg")
```






## Predictor 1: Populations

### Total Households

```{r}
DF = fread("data/nHouses1820_gu_qtrly.csv", encoding="UTF-8")
colnames(DF)[1] = "Month"
pop_TotalHouses1820_mly = DF %>% filter(Month >= "2018-01-01" & Month < "2020-07-01") %>% gather("gu", "TotalHouses", -Month) %>% arrange(gu, Month)
pop_TotalHouses1820_mly
```

Visualize
```{r}
pop_TotalHouses1820_mly %>% ggplot(aes(x=ymd(Month), y=log(TotalHouses), color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```



### Age ratio

```{r}
DF = fread("data/pop_age_long_qtrly.csv", encoding="UTF-8")
colnames(DF)[1] = "Month"
DF
```



```{r}
cor(DF[,3:ncol(DF)])
```



```{r}
pop_Age1820_mly = DF %>% select(Month, gu, age_05, age1929, age65_) %>% arrange(gu, Month)
pop_Age1820_mly
```

```{r}
pop_Age1820_mly %>% ggplot(aes(x=ymd(Month), y=log(age_05), color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```


### Household members ratio

```{r}
DF = fread("data/pop_housemember_mly.csv", encoding="UTF-8")
colnames(DF)[1] = "Month"
pop_Mem1820_mly = DF %>% select(Month, gu, mem1) %>% arrange(gu, Month)
pop_Mem1820_mly
```

```{r}
pop_Mem1820_mly %>% ggplot(aes(x=ymd(Month), y=mem1, color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```



### Average members

```{r}
DF = fread("data/PopPerHouse1820_gu_qtrly.csv", encoding = "UTF-8")
colnames(DF)[1] = "Month"
pop_AvgMem1820_mly = DF %>% filter(Month >= "2018-01-01" & Month < "2020-07-01") %>% gather("gu", "AvgMem", -Month) %>% arrange(gu, Month)
pop_AvgMem1820_mly
```

### Household income level

```{r}
pop_IncLv1820_mly = fread("data/incomelvl1820_gu_qtrly.csv", encoding = "UTF-8") %>% rename(Month = Qtr) %>% 
  filter(Month >= "2018-01-01" & Month < "2020-07-01") %>% gather("gu", "IncLv", -Month) %>% arrange(gu, Month)
pop_IncLv1820_mly$IncLv = pop_IncLv1820_mly$IncLv - 7 # seoul inc lvl 7
pop_IncLv1820_mly
```


## Predictor 2: Business

### Total restaurants
 
```{r}
buss_TotalBuss1820_mly = fread("data/nBuss1820_gu_qtrly.csv", encoding = "UTF-8") %>% rename(Month = Qtr) %>% 
  filter(Month >= "2018-01-01" & Month < "2020-07-01") %>% gather("gu", "nBusiness", -Month) %>% arrange(gu, Month)
buss_TotalBuss1820_mly
```

```{r}
buss_TotalBuss1820_mly %>% ggplot(aes(x=ymd(Month), y=log(nBusiness), color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```


### Business survival rate

```{r}
buss_Suv1yr1820_mly = fread("data/rSuv1yr1820_gu_qtrly.csv", encoding = "UTF-8") %>% rename(Month = Qtr) %>% 
  filter(Month >= "2018-01-01" & Month < "2020-07-01") %>% gather("gu", "Suv1yr", -Month) %>% arrange(gu, Month)
buss_Suv1yr1820_mly
```


## Predictor 3: Climate

### NO2
```{r}
cli_NO2_1820_mly = fread("data/pollutant_NO21820_monthly.csv", encoding = "UTF-8") %>% filter(Month <= "2020-06-01")
colnames(cli_NO2_1820_mly)[3] = "NO2"
cli_NO2_1820_mly
```


### pm10
```{r}
cli_pm10_1820_mly = fread("data/pollutant_pm101820_monthly.csv", encoding = "UTF-8") %>% filter(Month <= "2020-06-01")
colnames(cli_pm10_1820_mly)[3] = "pm10"
cli_pm10_1820_mly
```

### temperature

```{r}
cli_temp1820_mly = fread("data/avgtemp1820_mly.csv", encoding="UTF-8") %>% arrange(gu, Month)
cli_temp1820_mly
```


## Predictor 4: search trend

```{r}
search1820_mly = fread("data/search1820_mly.csv", encoding="UTF-8") %>% filter(Month <= "2020-06-01") %>% arrange(gu, Month)
search1820_mly
```

# All Combinded:

```{r}
DF = cbind(
  FW1820_mly,
  pop_TotalHouses1820_mly,
  pop_Age1820_mly,
  pop_Mem1820_mly,
  pop_AvgMem1820_mly,
  pop_IncLv1820_mly,
  buss_TotalBuss1820_mly,
  buss_Suv1yr1820_mly,
  cli_NO2_1820_mly,
  cli_pm10_1820_mly,
  cli_temp1820_mly,
  search1820_mly
)

DF = DF[,!duplicated(colnames(DF))] %>% filter(!(gu %in% c("강남구", "강북구")))
dim(DF)
DF
```

명절 넣기

```{r}
Holiday_dates = ymd(c("2018-02-01", "2019-02-01", "2020-01-01", "2018-09-01", "2019-09-01"))
Holidays = rep(0, nrow(DF))
for(i in 1:length(Holidays)){
  if(DF$Month[i] %in% Holiday_dates) Holidays[i] = 1
}
DF$Holidays = Holidays
DF
```


```{r}
write.table(DF, "data/FW1820_GU_MONTHLY.csv", sep=",", fileEncoding = "UTF-8", row.names = F)
fread("data/FW1820_GU_MONTHLY.csv", encoding = "UTF-8")
```



## Prediction

설명변수 TotalHouses, avg_temp, age_05, mem1, nBusiness 예측하기

0. TotalHouses

```{r}
pop_TotalHouses1820_mly %>% ggplot(aes(x=ymd(Month), y=log(TotalHouses), color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```
18년부터 20년까지의 추세가 지속될 것으로 가정.
```{r}
pop_TotalHouses1820_mly$month_int = rep(0:29, length(unique(pop_TotalHouses1820_mly$gu)))
ml = lmList(TotalHouses ~ I(month_int) | gu, pop_TotalHouses1820_mly)
intercepts = sapply(ml, coef)[1,]
slopes = sapply(ml, coef)[2,]
```

```{r}
DF_pred = as.data.frame(mapply(function(beta0, beta1, x) beta0+beta1*x, intercepts, slopes, MoreArgs = list(x=30:41)))
DF_pred$month_int = 30:41
DF_pred$Month = seq.Date(from=ymd("2020-07-01"), to=ymd("2021-06-01"), by="month")
DF_pred = DF_pred %>% gather("gu", "TotalHouses", -c(Month,month_int)) %>% select(Month, gu, TotalHouses)
```

```{r}
DF_real = pop_TotalHouses1820_mly %>% select(Month, gu, TotalHouses)
TTHpred = rbind(DF_real, DF_pred) %>% arrange(gu, Month)
TTHpred %>% ggplot(aes(x=ymd(Month), y=log(TotalHouses), color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```


1. age05

```{r}
pop_Age1820_mly %>% ggplot(aes(x=ymd(Month), y=log(age_05), color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```
18년부터 20년까지의 추세가 지속될 것으로 가정.
```{r}
pop_Age1820_mly$month_int = rep(0:29, length(unique(pop_Age1820_mly$gu)))
ml = lmList(age_05 ~ I(month_int) | gu, pop_Age1820_mly)
intercepts = sapply(ml, coef)[1,]
slopes = sapply(ml, coef)[2,]
```

```{r}
DF_pred = as.data.frame(mapply(function(beta0, beta1, x) beta0+beta1*x, intercepts, slopes, MoreArgs = list(x=30:41)))
DF_pred$month_int = 30:41
DF_pred$Month = seq.Date(from=ymd("2020-07-01"), to=ymd("2021-06-01"), by="month")
DF_pred = DF_pred %>% gather("gu", "age_05", -c(Month,month_int)) %>% select(Month, gu, age_05)
```

```{r}
DF_real = pop_Age1820_mly %>% select(Month, gu, age_05)
DF_real$Month = ymd(DF_real$Month)
AGE5pred = rbind(DF_real, DF_pred)
AGE5pred %>% ggplot(aes(x=ymd(Month), y=log(age_05), color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```

3. mem1

```{r}
pop_Mem1820_mly %>% ggplot(aes(x=ymd(Month), y=mem1, color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```
```{r}
pop_Mem1820_mly$month_int = rep(0:29, length(unique(pop_Mem1820_mly$gu)))
ml = lmList(mem1 ~ I(month_int) | gu, pop_Mem1820_mly)
intercepts = sapply(ml, coef)[1,]
slopes = sapply(ml, coef)[2,]
```

```{r}
DF_pred = as.data.frame(mapply(function(beta0, beta1, x) beta0+beta1*x, intercepts, slopes, MoreArgs = list(x=30:41)))
DF_pred$month_int = 30:41
DF_pred$Month = seq.Date(from=ymd("2020-07-01"), to=ymd("2021-06-01"), by="month")
DF_pred = DF_pred %>% gather("gu", "mem1", -c(Month,month_int)) %>% select(Month, gu, mem1)
```

```{r}
DF_real = pop_Mem1820_mly %>% select(Month, gu, mem1)
DF_real$Month = ymd(DF_real$Month)
MEM1pred = rbind(DF_real, DF_pred)
MEM1pred %>% ggplot(aes(x=ymd(Month), y=mem1, color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```

4. nBusiness

```{r}
buss_TotalBuss1820_mly %>% ggplot(aes(x=ymd(Month), y=nBusiness, color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```
```{r}
buss_TotalBuss1820_mly$month_int = rep(0:29, length(unique(buss_TotalBuss1820_mly$gu)))
ml = lmList(nBusiness ~ I(month_int) | gu, buss_TotalBuss1820_mly)
intercepts = sapply(ml, coef)[1,]
slopes = sapply(ml, coef)[2,]
```

```{r}
DF_pred = as.data.frame(mapply(function(beta0, beta1, x) beta0+beta1*x, intercepts, slopes, MoreArgs = list(x=30:41)))
DF_pred$month_int = 30:41
DF_pred$Month = seq.Date(from=ymd("2020-07-01"), to=ymd("2021-06-01"), by="month")
DF_pred = DF_pred %>% gather("gu", "nBusiness", -c(Month,month_int)) %>% select(Month, gu, nBusiness)
```

```{r}
DF_real = buss_TotalBuss1820_mly %>% select(Month, gu, nBusiness)
DF_real$Month = ymd(DF_real$Month)
NBSpred = rbind(DF_real, DF_pred)
NBSpred %>% ggplot(aes(x=ymd(Month), y=nBusiness, color=gu))+geom_line()+facet_wrap(~gu, scales = "free")
```


5. avg temp

```{r}
DF = cli_temp1820_mly %>% spread(gu, avg_temp)
DF
```

```{r}
avgtemp_mon = DF %>% select(Month, 강남구) %>% group_by(month(Month)) %>% summarize(mean=mean(강남구))
avgtemp_mon
```
```{r}
DFpred = data.frame(
  Month = seq.Date(from=ymd("2020-07-01"), to=ymd("2021-06-01"), by="month"),
  avg_temp = avgtemp_mon$mean[c(7:12, 1:6)]
)
DFpred
```

```{r}
n_gu = length(unique(cli_temp1820_mly$gu))
DFpred_long = DFpred %>% slice(rep(1:n(), each=n_gu))
DFpred_long$gu = rep(unique(cli_temp1820_mly$gu), nrow(DFpred))
DFpred_long = DFpred_long[,c(1,3,2)] %>% arrange(gu)
DFpred_long
```
```{r}
cli_temp1820_mly$Month = ymd(cli_temp1820_mly$Month)
TEMPpred = rbind(cli_temp1820_mly, DFpred_long)
TEMPpred %>% filter(gu == "강남구") %>% ggplot(aes(x=ymd(Month), y=avg_temp))+geom_line()
```

```{r}
DF = cbind(
  TTHpred,
  AGE5pred,
  MEM1pred,
  NBSpred,
  TEMPpred)

DF = DF[,!duplicated(colnames(DF))] %>% filter(!(gu %in% c("강남구", "강북구")))
dim(DF)
DF
```
```{r}
write.table(DF, "data/FW_pred.csv", sep=",", row.names=F, fileEncoding = "UTF-8")
```

```{r}
TTHpred
```



